### 2018-03-16 chapter4/ms.tex
Fixed most figures/tables. Table 5.3 still busted.

\begin{deluxetable}{lrccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{Summary of DECam Observations of GW151226
\label{ch4_datatable}}
\tablehead{
\colhead{Visit}    &
\colhead{UT}       &
\colhead{$\Delta t$\tablenotemark{a}} &
\colhead{$\langle$PSF$_i$$\rangle$}    &
\colhead{$\langle$PSF$_z$$\rangle$}    &
\colhead{$\langle$airmass$\rangle$}  &
\colhead{$\langle$depth$_i\rangle$}   &
\colhead{$\langle$depth$_z\rangle$}  &
\colhead{$A_{\mathrm{eff}}$\tablenotemark{b}} \\
\colhead{ } &
\colhead{ } &
\colhead{(days)} &
\colhead{(arcsec)} &
\colhead{(arcsec)} &
\colhead{ } &
\colhead{(mag)} &
\colhead{(mag)} &
\colhead{(deg$^2$)}
}
\startdata
 Epoch 1 & 2015-12-28.11 & 1.96 & 0.97 & 0.99 & 1.95 & 22.39 & 22.23 & 14.4 \\      %  6 hexes
               & 2015-12-29.11 & 2.96 & 1.00 & 0.97 & 1.78 & 22.57 & 22.46 & 14.4 \\      %  6 hexes
                \hline
 Epoch 2 & 2016-01-01.06 & 5.91 & 0.95 & 0.90 & 1.57 & 21.37 & 21.06 & 28.8 \\      % 12 hexes
 \hline
 Epoch 3 & 2016-01-08.11 & 12.96 & 1.68 & 1.62 & 2.15 & 22.09 & 21.70 & 24.0 \\      % 10 hexes
                & 2016-01-09.11 & 13.96 & 1.17 & 1.12 & 1.80 & 22.44 & 22.17 &  4.8 \\      %  2 hexes
                 \hline
 Epoch 4 & 2016-01-18.03 & 22.88 & 1.21 & 1.20 & 1.48 & 22.00 & 22.01 & 12.0 \\      %  5 hexes
               & 2016-01-19.01 & 23.86 & 1.29 & 1.25 & 1.71 & 21.86 & 21.90 & 16.8 \\ %  7 hexes
\enddata
\tablecomments{Summary of our DECam follow-up observations of
GW151226. The PSF, airmass, and depth are the average values across
all observations on that date. The reported depth corresponds to the mean
$5\sigma$ point source detection in the coadded search images.}
\tablenotetext{a}{Time elapsed between the GW trigger time and the time of the first image.}
\tablenotetext{b}{The effective area corresponds to 12 DECam pointings
taking into account that $\approx 20\%$ of the 3
deg$^2$ field of view of DECam is lost due to chip gaps (10\%), 3
dead CCDs (5\%, \citealt{Diehl+14}), and masked edge pixels (5\%).}
\end{deluxetable}

\begin{figure}[t!]
\centering
\vspace{-60pt}
\includegraphics[width=0.75 \textwidth]{./figs/chapter4/fig1.pdf}
\vspace{-60pt}
\caption{
Sky region covered by our DECam observations (red
hexagons) relative to the 50\% and 90\% probability regions
from the {\tt BAYESTAR} (cyan contours) and {\tt LALInference}
(white contours) localization of GW151226.
The background color indicates the estimated $5\sigma$
point-source limiting magnitude for a 90~s $i$-band exposure
as a function of sky position for the first night of our DECam
observations. The variation in the limiting magnitude is largely
driven by the dust extinction and airmass at that position.
The dark grey regions indicate sky positions that
were unobservable due to the telescope pointing limits.  The yellow contour
indicates the region of sky covered by the Dark Energy Survey
(DES). The total effective area for the 12 DECam pointings is 28.8
deg$^2$, corresponding to 3\%~(2\%) of the probability in the
{\tt BAYESTAR}~({\tt LALInference}) sky map.}
\label{fig:ch4_obs}
\end{figure}

@@

 \begin{figure}[t!]
 \centering
 \includegraphics[width=0.9\textwidth]{./figs/chapter4/fig2.pdf}
 \caption{\singlespace{\it Top}: Single-epoch images of our main candidate
 from all four epochs (green circle). This is the event discovered as PS15cdi in
 the PSST about 94 d prior to GW151226. {\it Bottom}: Light
 curve data for PS15cdi from PSST $w$- and $i$-band
 observations (green squares and yellow diamonds, respectively).
 Our DECam $i$- and $z$-band data are shown as
 blue circles and red stars, respectively. The revised DECam analysis
 using pre-existing templates is shown as open symbols. Upper
 limits are indicated by triangles. The inset focuses on our
 DECam data, indicating a rapid decline in both $i$ and $z$
 bands.  We fit a power-law model to the data finding a temporal index of
 $\alpha = -0.43$ (dashed-dot line). Kilonova models from Barnes and
 Kasen \citeyearpar{BarnesKasen13} with $v_{\rm ej}=0.2c$ and $M_{\rm ej}=0.1$ M$_\odot$
 at a distance of $187$~Mpc are also shown (dashed line).}
 \label{fig:ch4_PS15cdi}
 \end{figure}

>>>>

\begin{deluxetable}{lrccccccc}
\singlespace
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{Summary of DECam Observations of GW151226
\label{ch4_datatable}}
\tablehead{
\colhead{Visit}    &
\colhead{UT}       &
\colhead{$\Delta t$\tablenotemark{a}} &
\colhead{$\langle$PSF$_i$$\rangle$}    &
\colhead{$\langle$PSF$_z$$\rangle$}    &
\colhead{$\langle$airmass$\rangle$}  &
\colhead{$\langle$depth$_i\rangle$}   &
\colhead{$\langle$depth$_z\rangle$}  &
\colhead{$A_{\mathrm{eff}}$\tablenotemark{b}} \\
\colhead{ } &
\colhead{ } &
\colhead{(days)} &
\colhead{(arcsec)} &
\colhead{(arcsec)} &
\colhead{ } &
\colhead{(mag)} &
\colhead{(mag)} &
\colhead{(deg$^2$)}
}
\startdata
 Epoch 1 & 2015-12-28.11 & 1.96 & 0.97 & 0.99 & 1.95 & 22.39 & 22.23 & 14.4 \\      %  6 hexes
               & 2015-12-29.11 & 2.96 & 1.00 & 0.97 & 1.78 & 22.57 & 22.46 & 14.4 \\      %  6 hexes

 Epoch 2 & 2016-01-01.06 & 5.91 & 0.95 & 0.90 & 1.57 & 21.37 & 21.06 & 28.8 \\      % 12 hexes

 Epoch 3 & 2016-01-08.11 & 12.96 & 1.68 & 1.62 & 2.15 & 22.09 & 21.70 & 24.0 \\      % 10 hexes
                & 2016-01-09.11 & 13.96 & 1.17 & 1.12 & 1.80 & 22.44 & 22.17 &  4.8 \\      %  2 hexes

 Epoch 4 & 2016-01-18.03 & 22.88 & 1.21 & 1.20 & 1.48 & 22.00 & 22.01 & 12.0 \\      %  5 hexes
               & 2016-01-19.01 & 23.86 & 1.29 & 1.25 & 1.71 & 21.86 & 21.90 & 16.8 \\ %  7 hexes
\enddata
\tablecomments{Summary of our DECam follow-up observations of
GW151226. The PSF, airmass, and depth are the average values across
all observations on that date. The reported depth corresponds to the mean
$5\sigma$ point source detection in the coadded search images.}
\tablenotetext{a}{Time elapsed between the GW trigger time and the time of the first image.}
\tablenotetext{b}{The effective area corresponds to 12 DECam pointings
taking into account that $\approx 20\%$ of the 3
deg$^2$ field of view of DECam is lost due to chip gaps (10\%), 3
dead CCDs (5\%, \citealt{Diehl+14}), and masked edge pixels (5\%).}
\end{deluxetable}

\begin{figure}[t!]
\centering
\vspace{-60pt}
\includegraphics[width=0.75 \textwidth]{./figs/chapter4/fig1.pdf}
\vspace{-60pt}
\caption{\singlespace 
Sky region covered by our DECam observations (red
hexagons) relative to the 50\% and 90\% probability regions
from the {\tt BAYESTAR} (cyan contours) and {\tt LALInference}
(white contours) localization of GW151226.
The background color indicates the estimated $5\sigma$
point-source limiting magnitude for a 90~s $i$-band exposure
as a function of sky position for the first night of our DECam
observations. The variation in the limiting magnitude is largely
driven by the dust extinction and airmass at that position.
The dark grey regions indicate sky positions that
were unobservable due to the telescope pointing limits.  The yellow contour
indicates the region of sky covered by the Dark Energy Survey
(DES). The total effective area for the 12 DECam pointings is 28.8
deg$^2$, corresponding to 3\%~(2\%) of the probability in the
{\tt BAYESTAR}~({\tt LALInference}) sky map.}
\label{fig:ch4_obs}
\end{figure}

@@

 \begin{figure}[t!]
 \centering
 \includegraphics[width=0.9\textwidth]{./figs/chapter4/fig2.pdf}
 \caption{\singlespace \singlespace{\it Top}: Single-epoch images of our main candidate
 from all four epochs (green circle). This is the event discovered as PS15cdi in
 the PSST about 94 d prior to GW151226. {\it Bottom}: Light
 curve data for PS15cdi from PSST $w$- and $i$-band
 observations (green squares and yellow diamonds, respectively).
 Our DECam $i$- and $z$-band data are shown as
 blue circles and red stars, respectively. The revised DECam analysis
 using pre-existing templates is shown as open symbols. Upper
 limits are indicated by triangles. The inset focuses on our
 DECam data, indicating a rapid decline in both $i$ and $z$
 bands.  We fit a power-law model to the data finding a temporal index of
 $\alpha = -0.43$ (dashed-dot line). Kilonova models from Barnes and
 Kasen \citeyearpar{BarnesKasen13} with $v_{\rm ej}=0.2c$ and $M_{\rm ej}=0.1$ M$_\odot$
 at a distance of $187$~Mpc are also shown (dashed line).}
 \label{fig:ch4_PS15cdi}
 \end{figure}

### 2018-03-16 chapter5/ms.tex
Fixed most figures/tables. Table 5.3 still busted.

\tablecomments{Summary of photometry from \cref{sec:ch2_observations}. Dates are give in days relative to the time of the GW trigger (MJD = 57982.529). Photometry {\it is not} corrected for extinction. Limits are given at the $3\sigma$ level. Error bars are given at the $1\sigma$ level.}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=\textwidth]{./figs/chapter5/DECam_lc_alt.pdf}
\caption{UV, optical, and NIR Light curves of the counterpart of GW170817. The two-component model for $r$-process heating and opacities (\cref{sec:ch5_models}) is shown as solid lines. The right panels focus on the $g$ (top), $i$ (middle), and $H$-band photometry (bottom), over the first 10 nights. Triangles represent 3$\sigma$ upper limits. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_lc_good}
\end{center}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.55\textwidth]{./figs/chapter5/sed_col_bol_alt.pdf}
\caption{\singlespace{\it Top:} Optical colors from DECam observations as a function of time.  We observed rapid and early reddening in $g-r$ compared to the relatively flat but red $i-z$ colors. Also shown are template Ia SN colors relative to explosion for comparison \citep{Nugent+02}. {\it Middle:} SEDs at four representative epochs (assuming isotropic emission). The transition from a blue dominated spectrum at early times to a spectrum dominated by a red component at late times is clearly visible. {\it Bottom:} Bolometric light curve spanning $ugrizYH$. Expected values for $r$-process heating from \cite{Metzger+10} are shown for comparison, indicating that the observed emission requires ${\rm few}\times 10^{-2}$ M$_\odot$ of $r$-process ejecta. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_sed}
\end{center}
\end{figure}

@@

\begin{deluxetable}{cccccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{12}
\tablewidth{0pt}
\tablecaption{Kilonova Model Fits
	          \label{tab:ch5_KN}}
\tablehead{
\colhead{Model} &
\colhead{$M_{\rm ej}^{\rm blue}$} &
\colhead{$v_{\rm ej}^{\rm blue}$} &
\colhead{$\kappa^{\rm blue}$} &
\colhead{$M_{\rm ej}^{\rm purple}$} &
\colhead{$v_{\rm ej}^{\rm purple}$} &
\colhead{$\kappa^{\rm purple}$} &
\colhead{$M_{\rm ej}^{\rm red}$} &
\colhead{$v_{\rm ej}^{\rm red}$} &
\colhead{$\kappa^{\rm red}$} &
\colhead{$f^{\rm Ni}$} &
\colhead{WAIC} \\
\colhead{} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{}&
\colhead{}
}
\startdata
2-Comp & $0.014^{+0.002}_{-0.001}$ & $0.266^{+0.007}_{-0.002}$ & (0.5) & - & - & - & $0.036^{+0.001}_{-0.002}$ & $0.123^{+0.012}_{-0.014}$ & $3.349^{+0.364}_{-0.337}$  & - & -102 \\
3-Comp & $0.014^{+0.002}_{-0.001}$ & $0.267^{+0.006}_{-0.011}$ & (0.5) & $0.034^{+0.002}_{-0.002}$ & $0.110^{+0.011}_{-0.010}$ & (3.0) & $0.010^{+0.002}_{-0.001}$ & $0.160^{+0.030}_{-0.025}$ & (10.0) & - &  -106 \\
\hline
$^{56}$Ni & $0.008^{+0.007}_{-0.001}$ & $0.260^{+0.034}_{-0.031}$ & (0.1) & - & - & - & - & - & -  & $0.749^{+0.214}_{-0.203}$ & 17\\
Blue & $0.032^{+0.002}_{-0.004}$ & $0.180^{+0.002}_{-0.002}$ & (0.1) & - & - & - & - & - & -  & - & 17\\
Red & - & - & - & - & - & - & $0.026^{+0.010}_{-0.008}$ & $0.271^{+0.008}_{-0.002}$ & (10) & - & 153\\
1-Comp & - & - & - & $0.040^{+0.002}_{-0.007}$ & $0.274^{+0.007}_{-0.093}$ & $0.817^{+0.146}_{-0.135}$  & - & - & - & - &  11
\enddata
\tablecomments{Model parameters and WAIC scores. Numbers in parentheses indicate fixed parameters of the model. The errors represent the 1$\sigma$ confidence interval. Both the 2-component (``2-Comp'') and 3-component (``3-Comp'') models have significantly smaller WAIC scores (indicating better fits) compared to the four single-component models. }
\end{deluxetable}

@@

\begin{figure}
\begin{center}
\hspace*{-0.1in}
\scalebox{1.}
{\includegraphics[width=0.9\textwidth]{./figs/chapter5/lc_failed_alt.pdf}}
\caption{{\it Top Left:} Fitting the data with a Type I b/c SN model powered by the radioactive decay of $^{56}$Ni. This model clearly fails to capture the late time NIR behavior and requires an unphysically large fraction of the ejecta to be synthesized into nickel (\apx75\%). {\it Top Right:} Fitting the data with a single component ``blue'' KN model. Like the SN model, this fit is unable to capture the late time NIR behavior and overall spectra shape. {\it Bottom Left:} Fitting the data with a single component ``red'' KN model. This model clearly fails to capture any of the observed behavior. {\it Bottom Right:} Fitting the data with a single-component KN model with the opacity as a free parameter. Again, this model fails to capture the late time NIR behavior. This is suggestive of the fact that we need to model multiple ejecta components simultaneously. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_lc_failed}
\end{center}
\end{figure}

>>>>

\tablecomments{Summary of photometry from \cref{sec:ch5_observations}. Dates are give in days relative to the time of the GW trigger (MJD = 57982.529). Photometry {\it is not} corrected for extinction. Limits are given at the $3\sigma$ level. Error bars are given at the $1\sigma$ level.}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=\textwidth]{./figs/chapter5/DECam_lc_alt.pdf}
\caption{\singlespace UV, optical, and NIR Light curves of the counterpart of GW170817. The two-component model for $r$-process heating and opacities (\cref{sec:ch5_models}) is shown as solid lines. The right panels focus on the $g$ (top), $i$ (middle), and $H$-band photometry (bottom), over the first 10 nights. Triangles represent 3$\sigma$ upper limits. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_lc_good}
\end{center}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.55\textwidth]{./figs/chapter5/sed_col_bol_alt.pdf}
\caption{\singlespace \singlespace{\it Top:} Optical colors from DECam observations as a function of time.  We observed rapid and early reddening in $g-r$ compared to the relatively flat but red $i-z$ colors. Also shown are template Ia SN colors relative to explosion for comparison \citep{Nugent+02}. {\it Middle:} SEDs at four representative epochs (assuming isotropic emission). The transition from a blue dominated spectrum at early times to a spectrum dominated by a red component at late times is clearly visible. {\it Bottom:} Bolometric light curve spanning $ugrizYH$. Expected values for $r$-process heating from \cite{Metzger+10} are shown for comparison, indicating that the observed emission requires ${\rm few}\times 10^{-2}$ M$_\odot$ of $r$-process ejecta. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_sed}
\end{center}
\end{figure}

@@

\begin{landscape}
\resizebox{!}{\lineheight}{%
\singlespace
\begin{deluxetable}{cccccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{12}
\tablewidth{0pt}
\tablecaption{Kilonova Model Fits
	          \label{tab:ch5_KN}}
\tablehead{
\colhead{Model} &
\colhead{$M_{\rm ej}^{\rm blue}$} &
\colhead{$v_{\rm ej}^{\rm blue}$} &
\colhead{$\kappa^{\rm blue}$} &
\colhead{$M_{\rm ej}^{\rm purple}$} &
\colhead{$v_{\rm ej}^{\rm purple}$} &
\colhead{$\kappa^{\rm purple}$} &
\colhead{$M_{\rm ej}^{\rm red}$} &
\colhead{$v_{\rm ej}^{\rm red}$} &
\colhead{$\kappa^{\rm red}$} &
\colhead{$f^{\rm Ni}$} &
\colhead{WAIC} \\
\colhead{} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{($\text{M}_{\odot}$)} &
\colhead{(c)} &
\colhead{($\text{cm}^2 \text{g}^{-1}$)} &
\colhead{}&
\colhead{}
}
\startdata
2-Comp & $0.014^{+0.002}_{-0.001}$ & $0.266^{+0.007}_{-0.002}$ & (0.5) & - & - & - & $0.036^{+0.001}_{-0.002}$ & $0.123^{+0.012}_{-0.014}$ & $3.349^{+0.364}_{-0.337}$  & - & -102 \\
3-Comp & $0.014^{+0.002}_{-0.001}$ & $0.267^{+0.006}_{-0.011}$ & (0.5) & $0.034^{+0.002}_{-0.002}$ & $0.110^{+0.011}_{-0.010}$ & (3.0) & $0.010^{+0.002}_{-0.001}$ & $0.160^{+0.030}_{-0.025}$ & (10.0) & - &  -106 \\
\hline
$^{56}$Ni & $0.008^{+0.007}_{-0.001}$ & $0.260^{+0.034}_{-0.031}$ & (0.1) & - & - & - & - & - & -  & $0.749^{+0.214}_{-0.203}$ & 17\\
Blue & $0.032^{+0.002}_{-0.004}$ & $0.180^{+0.002}_{-0.002}$ & (0.1) & - & - & - & - & - & -  & - & 17\\
Red & - & - & - & - & - & - & $0.026^{+0.010}_{-0.008}$ & $0.271^{+0.008}_{-0.002}$ & (10) & - & 153\\
1-Comp & - & - & - & $0.040^{+0.002}_{-0.007}$ & $0.274^{+0.007}_{-0.093}$ & $0.817^{+0.146}_{-0.135}$  & - & - & - & - &  11
\enddata
\tablecomments{Model parameters and WAIC scores. Numbers in parentheses indicate fixed parameters of the model. The errors represent the 1$\sigma$ confidence interval. Both the 2-component (``2-Comp'') and 3-component (``3-Comp'') models have significantly smaller WAIC scores (indicating better fits) compared to the four single-component models. }
\end{deluxetable}}
\end{landscape}

@@

\begin{figure}
\begin{center}
\hspace*{-0.1in}
\scalebox{1.}
{\includegraphics[width=0.9\textwidth]{./figs/chapter5/lc_failed_alt.pdf}}
\caption{\singlespace {\it Top Left:} Fitting the data with a Type I b/c SN model powered by the radioactive decay of $^{56}$Ni. This model clearly fails to capture the late time NIR behavior and requires an unphysically large fraction of the ejecta to be synthesized into nickel (\apx75\%). {\it Top Right:} Fitting the data with a single component ``blue'' KN model. Like the SN model, this fit is unable to capture the late time NIR behavior and overall spectra shape. {\it Bottom Left:} Fitting the data with a single component ``red'' KN model. This model clearly fails to capture any of the observed behavior. {\it Bottom Right:} Fitting the data with a single-component KN model with the opacity as a free parameter. Again, this model fails to capture the late time NIR behavior. This is suggestive of the fact that we need to model multiple ejecta components simultaneously. Error bars are given at the $1\sigma$ level in all panels, but may be smaller than the points.}
\label{fig:ch5_lc_failed}
\end{center}
\end{figure}
